ODGI: scalable tools for pangenome graphs

### 2021-06-04 manuscript/main.tex
added financial support of SH
more motivation&biology, less bold statements, no API

    \abstract{ \textbf{Motivation:} Pangenomes graphs address some of the
      shortcomings of mainline genomics, in particular
      with regard to reference genome bias and identification of complex
      structural variants.
        %
        \\ \textbf{Results:} Here we present \odgi\, a novel range of
        scalable tools that implements new algorithms and has an efficient in-memory
        representation of DNA graphs. \odgi\ can handle hundreds of
        large genomes in memory with fast parallel execution. \odgi\ includes
        tools for detecting complex regions, extracting \textit{loci}, removing artifacts,
        exploratory analysis, and graph sorting, manipulation and visualisation.
        \odgi\ also provides an extensible API that allows for writing new tool.
        %
        \\
        \textbf{Availability:} \odgi\ is software written in the \Cpp\ programming language and
        published under the permissive MIT license. Source code and documentation can be downloaded from
        \href{https://github.com/pangenome/odgi}{https://github.com/pangenome/odgi}.\\
        %
        \textbf{Contact:}
        % \href{andreaguarracino@outlook.com}{andreaguarracino@outlook.com},
        egarris5@uthcs.edu
        \\
        \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online. \FIXME
        }
    \maketitle

>>>>

    \abstract{ \textbf{Motivation:} Pangenomes graphs address some of the
      shortcomings of mainline genomics, in particular
      with regard to reference genome bias and identification of complex
      structural variants. Hence, fast and versatile software is required to ask intricate questions of such data in an efficient way.
        %
        \\ \textbf{Results:} Here we present \odgi\ a novel range of scalable tools that implements new algorithms and has an efficient in-memory representation of DNA graphs. \odgi\ includes tools for detecting complex regions, extracting \textit{loci}, removing artifacts, exploratory analysis, and graph sorting, manipulation and visualisation. Its fast parallel execution facilitates routine pangenomic tasks as well as pipelines that can quickly answer complex biological questions of very large pangenome graphs.
        %
        \\
        \textbf{Availability:} \odgi\ is \Cpp\ software
        published under the permissive MIT license. Source code and documentation are available at
        \href{https://github.com/pangenome/odgi}{https://github.com/pangenome/odgi}.\\
        %
        \textbf{Contact:}
        % \href{andreaguarracino@outlook.com}{andreaguarracino@outlook.com},
        egarris5@uthcs.edu
        \\
        \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online. \FIXME
        }
    \maketitle
